Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-04 doc/paper.Rmd
reference to joint-slip pliers

\begin{enumerate}
\item Problem statement: same source matching based on striations
\item Existing solution for toolmarks: Chumbley Score 
\item How is the chumbley score computed? 
\item Potential limitations in the application to striation marks on bullet lands: smaller in width and curved - need to adjust parameter settings
\item Using cross-validation setup to identify appropriate parameter settings for (a) signatures and (b) profiles directly
\end{enumerate}

@@

WO 320 wv 50
```{r echo=FALSE}
a<- matrix(NA, ncol = 3, nrow = 2)
bullet.falsepositive<- data.frame(a)
colnames(bullet.falsepositive)<- c("Classification", "FALSe", "TRUe")
bullet.falsepositive$Classification<- c("FALSe", "TRUe")
bullet.falsepositive$FALSe<- c(77564,412)
bullet.falsepositive$TRUe<- c(4022,674)
bullet.falsepositive

```
Wo 200 WV 50
```{r echo=FALSE}
bullet.falsepositive$FALSe<- c(78817,383)
bullet.falsepositive$TRUe<- c(4004,798)
bullet.falsepositive

```
Wo 80 wv 50
```{r echo=FALSE}
bullet.falsepositive$FALSe<- c(78817,450)
bullet.falsepositive$TRUe<- c(4680,775)
bullet.falsepositive

@@

>>>>

\begin{enumerate}
\item Problem statement: same source matching based on striations
\item Existing solution for toolmarks: Chumbley Score 
\item How is the chumbley score computed? 
\item Potential limitations in the application to striation marks on bullet lands: smaller in width and curved - need to adjust parameter settings; something similar is done in \citet{afte-chumbley} for toolmark comparisons of slip-joint pliers.
\item Using cross-validation setup to identify appropriate parameter settings for (a) signatures and (b) profiles directly
\end{enumerate}

@@

WO 320 wv 50
```{r echo=FALSE}
# a<- matrix(NA, ncol = 3, nrow = 2)
# bullet.falsepositive<- data.frame(a)
# colnames(bullet.falsepositive)<- c("Classification", "FALSe", "TRUe")
# bullet.falsepositive$Classification<- c("FALSe", "TRUe")
# bullet.falsepositive$FALSe<- c(77564,412)
# bullet.falsepositive$TRUe<- c(4022,674)
# bullet.falsepositive

all %>% filter(wo==320, wv==50) %>% xtabs(data=., ~signif+match)
```
Wo 200 WV 50
```{r echo=FALSE}
# bullet.falsepositive$FALSe<- c(78817,383)
# bullet.falsepositive$TRUe<- c(4004,798)
# bullet.falsepositive

all %>% filter(wo==200, wv==50) %>% xtabs(data=., ~signif+match)
```
Wo 80 wv 50
```{r echo=FALSE}
# bullet.falsepositive$FALSe<- c(78817,450)
# bullet.falsepositive$TRUe<- c(4680,775)
# bullet.falsepositive

all %>% filter(wo==80, wv==50) %>% xtabs(data=., ~signif+match)

@@

```{r wo120, fig.width = 8, fig.height=4.5}
wo120 <- errors %>% filter(wo==120)
wo120 %>% gather(type, error, actual:beta) %>%
  ggplot(aes(x = wv, y = error, colour = factor(alpha)))  + 
  geom_line() + geom_point() + facet_wrap(~type, scales="free") +
  theme_bw()+ 
  theme(legend.position="bottom")
```
